Composition-climate paper

### 2014-12-04 Composition_Ecology.Rmd
Getting the repo set up. * Added `ecology.csl` to allow formatting of `bib` files. * moved in the goringetal bib file, assuming many refs will cross-over. * Added `margins.sty` to set out the pre-formatting for the rendered document. * started commenting `resampling_climate` *  Added the header blob for the paper.

Land use patterns and historical contingency change climate optima for key forest genera in the Northeastern United States.
========================================================
What is the climate space of the northeastern United States?

>>>>

---
title: "Composition-climate paper"
author: "Simon Goring *et al*."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
pdf_document:
pandoc_args: "-H margins.sty"
bibliography: composition.bib
csl: harvard1.csl
---

Land use patterns and historical contingency change climate optima for key forest genera in the Northeastern United States.
========================================================

*Historic land use and forest change over the centuries since Euroamerican settlement have significantly changed
